---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ycevo

<!-- badges: start -->
[![R-CMD-check](https://github.com/bonsook/ycevo/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bonsook/ycevo/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/ycevo)](https://CRAN.R-project.org/package=ycevo)
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
<!-- [![metacran downloads](https://cranlogs.r-pkg.org/badges/ycevo)](https://cran.r-project.org/package=ycevo) -->
<!-- badges: end -->

The goal of `ycevo` is to provide means for the non-parametric estimation of the discount function and yield curve of bonds.

If you use any data or code from the `ycevo` package CRAN release in a publication, please use the following citation:  

> Bonsoo Koo, and Yangzhuoran Fin Yang (2022). ycevo: Non-Parametric Estimation
of the Yield Curve Evolution. R package version 0.1.2. https://CRAN.R-project.org/package=ycevo. 

The package provides code used in Koo, La Vecchia, & Linton (2021). Please use the following citation if you use any result from the paper.

> Koo, B., La Vecchia, D., & Linton, O. (2021). Estimation of a nonparametric model for bond prices from cross-section and time series information. Journal of Econometrics, 220(2), 562-588.

## Development cycle

The package is in active development and it have been experiencing substantial changes.
Since the existing forks have remained inactive for several years, significant modifications have been implemented through rebase. It is advisable for any existing forks to undergo the rebase process.
```
git remote add upstream https://github.com/bonsook/ycevo.git
git fetch upstream
git rebase upstream/master
git push origin master --force
```

## Installation

You can install the __released__ version of ycevo from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("ycevo")
```

You can install the __development__ version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bonsook/ycevo")
```
<!-- ## Usage -->

```{r}
#| eval: false
#| echo: false
library(ycevo)
library(dplyr)
library(tidyr)
library(ggplot2)
library(lubridate)

# Simulate 4 bonds issued at 2020-01-01
# with maturity 180, 360, 540, 720 days
# Apart from the first one, 
# each has coupon 2, 
# of which half is paid every 180 days.
# The yield curve is sumulated fron `get_yield_at_vec`
# Quotation date is also at 2020-01-01
exp_data <- tibble(
  qdate = ymd("2020-01-01"), 
  id = rep(1:4, 1:4), 
  pdint = c(100, 1, 101, 1, 1, 101, 1, 1, 1, 101),
  tupq = unlist(sapply(1:4, seq_len)) * 180, 
  accint = 0
) %>% 
  mutate(discount = exp(-tupq/365 * get_yield_at_vec(0, tupq/365))) %>% 
  group_by(id) %>% 
  mutate(price = sum(pdint * discount)) %>% 
  ungroup()

# Only one quotation so time grid is set to 1
xgrid <- 1 
# Discount function is evaluated at time to maturity of each payment in the data
tau <- unique(exp_data$tupq/365) 

# Estimated yield and discount
yield <- ycevo(
  exp_data, 
  xgrid = xgrid,
  tau = tau
)
yield 

# True yield
get_yield_at_vec(0, tau)

# Plot of yield curve
yield %>%
  mutate(true_yield = get_yield_at_vec(0, tau)) %>% 
  pivot_longer(c(yield, true_yield)) %>% 
  mutate(xgrid = round(xgrid, 2)) %>%
  ggplot() + 
  geom_line(aes(x = tau, y = value)) +
  facet_wrap(name~xgrid, labeller = label_both)

# Plot of discount function
yield %>%
  mutate(true_discount = exp(-tau * get_yield_at_vec(0, tau))) %>% 
  pivot_longer(c(discount, true_discount)) %>% 
  mutate(xgrid = round(xgrid, 2)) %>%
  ggplot() + 
  geom_line(aes(x = tau, y = value)) +
  facet_wrap(name~xgrid, labeller = label_both)
```


## License

This package is free and open source software, licensed under GPL-3
