---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ycevo

<!-- badges: start -->
[![R-CMD-check](https://github.com/bonsook/ycevo/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bonsook/ycevo/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/ycevo)](https://CRAN.R-project.org/package=ycevo)
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
<!-- [![metacran downloads](https://cranlogs.r-pkg.org/badges/ycevo)](https://cran.r-project.org/package=ycevo) -->
<!-- badges: end -->

The goal of `ycevo` is to provide means for the non-parametric estimation of the discount function and yield curve of bonds.

If you use any data or code from the `ycevo` package CRAN release in a publication, please use the following citation:  

> Bonsoo Koo, and Yangzhuoran Fin Yang (2024). ycevo: Non-Parametric Estimation
of the Yield Curve Evolution. R package version 0.2.1. https://CRAN.R-project.org/package=ycevo. 

The package provides code used in Koo, La Vecchia, & Linton (2021). Please use the following citation if you use any result from the paper.

> Koo, B., La Vecchia, D., & Linton, O. (2021). Estimation of a nonparametric model for bond prices from cross-section and time series information. Journal of Econometrics, 220(2), 562-588.

## Development cycle

The package is in active development and it have been experiencing substantial changes.
Since the existing forks have remained inactive for several years, significant modifications have been implemented through rebase. It is advisable for any existing forks to undergo the rebase process.
```
git remote add upstream https://github.com/bonsook/ycevo.git
git fetch upstream
git rebase upstream/master
git push origin master --force
```

## Installation

You can install the __released__ version of ycevo from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("ycevo")
```

You can install the __development__ version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bonsook/ycevo")
```
## Usage

```{r}
library(ycevo)
library(lubridate)

## Simulate
set.seed(1)
bonds <- ycevo_data()
bonds
```


```{r}
#| eval: false
## Estimate at specified time points
x <- seq(ymd("2023-03-01"), ymd("2023-08-01"), by = "1 month")
res <- ycevo(bonds, x)
## Supports parallel processing and progress bar
# future::plan(future::multisession)
# res <- progressr::with_progress(ycevo(bonds, x))
```
```{r}
#| echo: false
x <- seq(ymd("2023-03-01"), ymd("2023-08-01"), by = "1 month")
future::plan(future::multisession)
res <- ycevo(bonds, x)
```
```{r}
res
```


```{r}
## Predict
augment(res)

## Plot
autoplot(res)
```


```{r}
#| eval: false
## Compare to the true yield curve
curve_true <- list()
for(i in seq_along(x)) {
  curve_true[[i]] <- tibble(
    tau=1:20, 
    qdate = x[[i]],
    .yield = get_yield_at((x[[i]] - ymd("2023-01-01"))/365, tau), 
    .discount = exp(-tau * .yield))
}
curve_true <- bind_rows(curve_true)
curve_true <- pivot_longer(
  curve_true, 
  c(.discount, .yield), 
  names_to = ".est", 
  values_to = ".value")

autoplot(res) +
  geom_line(data = curve_true, linetype = "dashed")

```


## License

This package is free and open source software, licensed under GPL-3
