---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ycevo

<!-- badges: start -->
  [![Build Status](https://travis-ci.org/bonsook/ycevo.svg?branch=master)](https://travis-ci.org/bonsook/ycevo)
<!-- badges: end -->

The goal of ycevo is to provide a range of functions to facilitate the non-parametric estimation of the discount rate, and yield curve, of CRSP Bond Data.

If you use any data or code from the `ycevo` package in a publication, please use the following citation:  
 
> Bonsoo Koo, Nathaniel Tomasetti, Kai-Yang Goh and Yangzhuoran Yang (2019). ycevo: Non-Parametric Estimation
  of the Yield Curve Evolution. R package version 1.0.0. https://github.com/bonsook/ycevo. 

The package provides code used in Koo, La Vecchia, & Linton (2019). Please use the following citation if you use any result from the paper.

> Koo, B., La Vecchia, D., & Linton, O. B. (2019). Estimation of a Nonparametric model for Bond Prices from Cross-section and Time series Information. Available at SSRN3341344.

## Installation

<!-- You can install the released version of ycevo from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("ycevo") -->
<!-- ``` -->
The __stable__ version on CRAN is coming soon.

The __development__ version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bonsook/ycevo")
```
## Usage

```{r}
library(ycevo)
library(tidyverse)
library(lubridate)# Twelve quotation dates
max_qDate <- 12
#Estimate a 36 period ahead yield curve for each qdate
periods <- 36

set.seed(1)
data <- simulate_data(max_qDate = max_qDate, periods = periods)
glimpse(data)
# grid values
ugrid <- (1:(max_qDate - 2))/(max_qDate - 1)
# bandwidth for each grid value
hu <- rep(0.5 /  max_qDate, max_qDate -2)

qgrid <- 1:periods
max_tumat <- max(data$tumat)
qgrid <- qgrid[1:min(which(qgrid >= max_tumat))]
hq <- rep(0.1, length(qgrid))

xgrid <- qgrid
hx <- hq

yield <- estimate_yield(
    data = data,
    ugrid = ugrid,
    hu = hu,
    xgrid = xgrid,
    hx = hx,
    qgrid = qgrid,
    hq = hq,
    units = 1, 
    loess = FALSE)
glimpse(yield)

# Yield vs Time (qgrid)
yield %>%
  mutate(ug = round(ug, 2)) %>%
  ggplot() + geom_line(aes(qg, yield)) +
  facet_wrap(~ug) +
  theme_bw()

# Yield vs Quotation Dates (ugrid) for some time to maturities

select_qgrid <- c(3, 12, 24, 36)

yield %>%
  filter(qg %in% select_qgrid) %>%
  ggplot() + geom_line(aes(ug, yield)) +
  facet_wrap(~qg) +
  theme_bw()
```


## License

This package is free and open source software, licensed under GPL-3
