---
title: "Introduction to ycevo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to ycevo}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## Introduction

The goal of ycevo is to provide a range of functions to facilitate the non-parametric estimation of the discount rate, and yield curve, of CRSP Bond Data.

If you use any data or code from the `ycevo` package in a publication, please use the following citation:  
 
> Bonsoo Koo, Nathaniel Tomasetti, Kai-Yang Goh and Yangzhuoran Yang (2019). ycevo: Non-Parametric Estimation
  of the Yield Curve Evolution. R package version 1.0.0. https://github.com/FinYang/ycevo. 

The package provides code used in Koo, La Vecchia, & Linton (2019). Please use the follwing citation if you use any result from the paper.

> Koo, B., La Vecchia, D., & Linton, O. B. (2019). Estimation of a Nonparametric model for Bond Prices from Cross-section and Time series Information. Available at SSRN3341344.

## Simulation Example

Load in the libraries we will use.
```{r, message = FALSE}
library(ycevo)
library(tidyverse)
library(lubridate)
```

The data must be provided as a data.frame or tibble object, with one row corresponding to each payment - either the coupon or principal - for one bond on one quotation date.
The functions require particular column names:

* qdate: The quotation date, as an integer or lubridate::date object

* crspid: Some character or factor that uniquely identifies the bond

* mid.price: the quoted price of the bond on that day

* tupq: Time until a given payment, usually given in days

* tumat: Time until maturity, in days (equal to tupq for zero coupon bonds)

* pdint: Numeric value of payment

* accint: The accumulated interest on payments

For example, if a bond traded on 18/9/2019 has five payments remaining until maturity, it should have five rows in the data with a quotation date of 18/9/2019. Each of these five rows will have a different value of pdint and tupq, corresponding to the five payments, but will have the same value for price, accint, and tumat

The CRSP bond database for 2007 is provided as USbonds as an example
```{r}
glimpse(USbonds)
```
Several columns in the data are purely descriptive.


Alternatively we can simulate some data, with twelve quotation dates, where we want to estimate a thirty six period ahead yield curve for each of these dates. The function will first generate some yield curves for each quotation date, and simulate fake bond data with prices corresponding to these yields. We can extract the yield curves using the `generate_yield()` function.
```{r}
# Twelve quotation dates
max_qDate <- 12
#Estimate a 36 period ahead yield curve for each qdate
periods <- 36

set.seed(1)
data <- simulate_data(max_qDate = max_qDate, periods = periods)
glimpse(data)
```

We want to estimate the yield curve at various quotation dates to find how it evolves over time.

First we need to define `ugrid`, the grid of quotation dates that we want to estimate the discount rate for. `ugrid` is provided as a decimal from 0 to 1. A `ugrid` of 0 indicates the first available day in the data, and a `ugrid` of 1 indicates the last available day. The first line will create max_qDate - 2 = 10 `ugrid` values spread evenly throughout the 12 quotation dates in the data. Each `ugrid` value is associated with a bandwidth. Quotation dates within `ugrid` $\pm$ `hu` will be included in the calculations, with the epaker kernel function. 
It works best if the intervals defined by `ugrid` $\pm$ `hu` do not include zero or one.

```{r}
# grid values
ugrid <- (1:(max_qDate - 2))/(max_qDate - 1)
# bandwidth for each grid value
hu <- rep(0.5 /  max_qDate, max_qDate -2)
```

Next we need a grid of the time-to-payment values that we want to estimate a discount rate for! This grid is referred to as `qgrid`. Some of the functions used below have a units argument. If qgrid is in the same unit as tupq is (e.g., days), set units to 1. If tupq is in days and you want to specify qgrid in years, set units to 365. Each value of qgrid plus/minus hq defines a bin. It is okay if there is no observed payments for some of these bins (we will interpolate nearby payments) but the first and last bin needs to contain some payment. We include a few lines here to check the latest bond in the data, and truncate qgrid to this value.

```{r}
qgrid <- 1:periods
max_tumat <- max(data$tumat)
qgrid <- qgrid[1:min(which(qgrid >= max_tumat))]
hq <- rep(0.1, length(qgrid))
```

We also need a different grid of time-to-payment values for some cross-product terms. This is called `xgrid`, and for now we will keep it equal to `qgrid`. Later on, we will introduce a function to automatically select `xgrid` values. 
```{r}
xgrid <- qgrid
hx <- hq
```

The main function of the package is `estimate_yield`. We may run this once, with all of our grids, under certain conditions:

1. `ugrid` is input as a vector

2. `qgrid` is a vector, and will be kept constant for every value of `ugrid`, OR, `qgrid` is a matrix and a different row of `qgrid` is used for each `ugrid`.

3. `xgrid` is a vector, and will be kept constant for every value of `ugrid`, OR, `xgrid` is a matrix and a different row of `xgrid` is used for each `ugrid`.

This provides a dataframe containing the discount rate and yield at each `ugrid` / `qgrid` combination. `estimate_yield` may take several minutes to run for real data.

```{r}
yield <- estimate_yield(
    data = data,
    ugrid = ugrid,
    hu = hu,
    xgrid = xgrid,
    hx = hx,
    qgrid = qgrid,
    hq = hq,
    units = 1)
glimpse(yield)
```

`ug`, `rg`, and `xg` correspond to `ugrid`, `rgrid`, and `xgrid`. If you didn't provide an `rgrid`, `hr` will not appear in the result. For each combination of these, we have the discount rate `discount` and yield `yield`.

Lets make a few plots of the results.

```{r}
# Yield vs Time (qgrid)
yield %>%
  mutate(ug = round(ug, 2)) %>%
  ggplot() + geom_line(aes(qg, yield)) +
  facet_wrap(~ug) +
  theme_bw()
```

```{r}
# Yield vs Quotation Dates (ugrid) for some time to maturities

select_qgrid <- c(3, 12, 24, 36)

yield %>%
  filter(qg %in% select_qgrid) %>%
  ggplot() + geom_line(aes(ug, yield)) +
  facet_wrap(~qg) +
  theme_bw()
```



## License

This package is free and open source software, licensed under GPL-3